`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2016-12-19 inst/manuscript/manuscript.rmd
Switch to CRAN as targeted hosting archive;

# Availablility and Implementation {-}
`flippant` has been implemented in `R` [@r_core_team_r:_2016] and integrated 
into the `Bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install-- and loadable as follows from 
within a functional `R` environment:

```{r noeval_demonstrate_installation, eval = FALSE}
source("http://bioconductor.org/biocLite.R")
biocLite(pkgs = "flippant")
library("flippant")
```

>>>>

# Availablility and Implementation {-}
`flippant` has been implemented in `R` [@r_core_team_r:_2016] and Is available
"Comprehensive `R` Archive Network" (CRAN). It is thus install-- and loadable as
follows from within a functional `R` environment:

```{r noeval_demonstrate_installation, eval = FALSE}
install.packages("flippant")
library("flippant")
```
